\documentclass[11pt]{res} % default is 10 pt
\usepackage{hyperref}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font
\setlength{\textheight}{9.5in} % increase text height to fit resume on 1 page
\newsectionwidth{0pt}  % So the text is not indented under section headings

\begin{document}

\name{Arash Rouhani\\[12pt]} % the \\[12pt] adds a blank line after name

\address{{\bf } \\ Arash Rouhani
                \\ 464:22 Omg{\aa}ngen
                \\ 412 80 Gothenburg, Sweden}
\address{{\bf } \begin{tabular}[t]{ l l }
                       \\ Email:  & Arash.Rouhani@gmail.com
                       \\ Mobile: & +4676 2323 775
                \end{tabular} }

\begin{resume}

\section{PROFESSIONAL QUALIFICATIONS}
   \begin{itemize} % \itemsep -2pt  % reduce space between items
   \item Second best Swedish participant in
    Google Code Jam 2010 and TopCoder Open 2010.
   \item Won the national Informatics Olympiad 2009.
    Represented Sweden in the International Olympiad in Informatics (IOI), Bulgaria 2009.
   \item Versed in many programming languages (Haskell, C++, C\#, Java, Delphi)
    and have tried out many paradigms
    (Reactive, Concurrency-Based, Logical).
   \item Linux user. Daily collaborating on open source projects
    at \href{https://github.com/Tarrasch}{github},
    such as the Yesod Web Framework (haskell) and
    various other haskell-libraries as well as my own projects.
   \item Maintaining a Jenkins continuous integration server
    and webmastering my university's student website.
   \item Currently a supplemental instruction leader in math at the university.
   \item Speaking four languages: Swedish, English, Farsi and (some) German.
 \end{itemize}

\section{EDUCATION}
 \noindent Completed 3 of 5 years of M.Sc. in CS
  at Chalmers University of Technology.

\section{WORKING EXPERIENCE}
\emph{Spotify, Software Engineer Intern, June-August 2011}, Stockholm, Sweden
\vspace{0.2in}
   \begin{itemize} % \itemsep -2pt  % reduce space between items
   \item Designed and implemented a large test suite for their C API libspotify
   which significantly increased the code coverage. Many bugs were detected as
   a result, some of which I fixed.

 \end{itemize}


\emph{Silobreaker, Software Engineer Intern, June-August 2010 and 2009}, Stockholm, Sweden
\vspace{0.2in}
 \begin{itemize} % \itemsep -2pt  % reduce space between items
  \item Built a mobile site, used Support Vector Machines, wrote a tokenizer,
   programmed a GUI.
  \item Became acquainted with Scrum and Test Driven Development.
\end{itemize}

\section{OTHER MERITS}

   \begin{itemize} % \itemsep -2pt  % reduce space between items
   \item European Robotics Championship 2010 in Vienna.
    Participated with a autonomous line-following robot.
   \item Coorganizing the informatics contest in Sweden.
    I've authored almost 20 tasks (with solutions and input data)
    and traveled to Estonia (2010) and Denmark (2011) as a team leader
    with the Swedish IOI team.
 \end{itemize}

\section{ACTIVITIES}

I enjoy Chess, play squash and practice the harmonica.
I regularly participate in extracurricular
activities at the university.


\end{resume}
\end{document}











