\documentclass[11pt]{res} % default is 10 pt
\usepackage{hyperref}
\setlength{\textheight}{9.5in} % increase text height to fit resume on 1 page
\newsectionwidth{0pt}  % So the text is not indented under section headings

\begin{document}

\name{Arash Rouhani} % the \\[12pt] adds a blank line after name

\address{{\bf } \begin{tabular}[t]{l l}
                       \\ \href{mailto:Arash.Rouhani@gmail.com}{Arash.Rouhani@gmail.com}
                \end{tabular} }
\address{{\bf } \begin{tabular}[t]{l l}
                       \\ \href{http://arashrouhani.com}{arashrouhani.com}
                \end{tabular} }

\begin{resume}

\section{PROFESSIONAL QUALIFICATIONS}
   \begin{itemize} % \itemsep -2pt  % reduce space between items
   \item
     Chief Maintainer of \href{https://github.com/spotify/luigi}{luigi}, a
     very popular open source task orchestrator.
   \item Second best Swedish participant in
    Google Code Jam 2010 and TopCoder Open 2010.
   \item Won the national Informatics Olympiad 2009.
    Represented Sweden in the International Olympiad in Informatics (IOI), Bulgaria 2009.
   \item Versed in many programming languages (Haskell, C++, C\#, Java, Python, Ruby)
    and have tried out many paradigms
    (Reactive, Concurrency-Based, Logical).
   \item Linux user. I use
    \href{https://github.com/Tarrasch}{github} on a daily basis and I have written many
    \href{https://github.com/search?q=\%40Tarrasch+zsh+OR+antigen\&type=Repositories\&ref=searchresults}{zsh shell plugins}.
   % \item Maintaining a Jenkins CI server and webmastering my university's
   %   student website.
   % \item Been a supplemental instruction leader and teaching assistant in
   %   various courses.
   % \item Speaking four languages: Swedish, English, Farsi and (some) German.
 \end{itemize}

\section{EDUCATION}
 \begin{itemize} % \itemsep -2pt  % reduce space between items
   % \item Master's degree in Algorithms, Languages and Logic from Chalmers
   %   (2013-2014).
   \item Master's degree in Algorithms, Languages and Logic from Chalmers
     (2009-2014).
   \item Graduate level exchange student at Georgia Tech (2012-2013).
   % \item Bachelor's degree in CSE from Chalmers University of Technology
   %   (2009-2012).
 \end{itemize}

\section{WORKING EXPERIENCE}
\emph{Spotify}, {\footnotesize Developer, April 2014 and ongoing}, Stockholm, Sweden
\vspace{0.2in}
   \begin{itemize}
     \item I help other teams become more data-driven by developing tools and
     providing guidance.  In particular I work a lot with Luigi and Apache
     Crunch.
 \end{itemize}

\emph{Facebook}, {\footnotesize Software Engineer Intern, May-August 2013}, Menlo Park, California
\vspace{0.2in}
   \begin{itemize}
   \item I worked on an internal job scheduler and interfaced with HBase. The
     scheduler used reactive programming to handle that HBase region mappings
     can change. I replaced a map reduce job with one using the internal
     scheduler. The internal scheduler were two times as fast.
 \end{itemize}

 \emph{Spotify}, {\footnotesize Software Engineer Intern, June-August 2012 and 2011}, Stockholm, Sweden
\vspace{0.2in}
   \begin{itemize} % \itemsep -2pt  % reduce space between items
   \item In 2011 I designed and implemented a large test suite for their C API
     libspotify which significantly increased the code coverage. Many bugs were
     detected as a result, some of which I fixed. In 2012 I resolved
     concurrency issues their client program had. As a result, they now can use
     continuous integration and trust it, since the bug fixes removed
     intermittent failures.

 \end{itemize}


 \emph{Silobreaker}, {\footnotesize Software Engineer Intern, June-August 2010 and 2009}, Stockholm, Sweden
\vspace{0.2in}
 \begin{itemize} % \itemsep -2pt  % reduce space between items
  \item Built a mobile site, used Support Vector Machines, wrote a tokenizer,
   programmed a GUI.
  \item Became acquainted with Scrum and Test Driven Development.
\end{itemize}

\section{OTHER MERITS}

\begin{itemize} % \itemsep -2pt  % reduce space between items
    % \item European Robotics Championship 2010 in Vienna.
    %  Participated with a autonomous line-following robot.
  \item Organizing the informatics contest in Sweden.  I've authored about
    30 tasks (with solutions and input data) and traveled to Estonia (2010),
    Denmark (2011), Latvia (2012), Taiwan (2014) and Kazakhstan (2015) as a
    team leader with the Swedish IOI team.
\end{itemize}

\end{resume}
\end{document}
