\documentclass[11pt]{res} % default is 10 pt
\usepackage{hyperref}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textheight}{9.5in} % increase text height to fit resume on 1 page
\newsectionwidth{0pt}  % So the text is not indented under section headings

\begin{document} 
 
\name{Arash Rouhani\\[12pt]} % the \\[12pt] adds a blank line after name

\address{{\bf } \\ Arash Rouhani
                \\ 464:22 Omg{\aa}ngen
                \\ 412 80 Gothenburg, Sweden}
\address{{\bf } \begin{tabular}[t]{ l l }
                       \\ Email:  & Arash.Rouhani@gmail.com
                       \\ Mobile: & +4676 2323 775
                       \\ DOB:    & 1990-11-17 
                \end{tabular} }
                                             
\begin{resume}
                                               
\section{PROFESSIONAL QUALIFICATIONS} 
   \begin{itemize} % \itemsep -2pt  % reduce space between items
   \item Second best Swedish participant in
    Google Code Jam 2010 and TopCoder Open 2010,
    the two main algorithm competitions.
    The competitions consist of solving problems in a few hours.
   \item Won the national Programming Olympiad for high school students.
    Represented Sweden in the Programming Olympiad in Bulgaria 2009.
   \item Versed in many programming languages and different paradigms,
    particularly Haskell.
   \item Linux user. Daily collaborating on open source projects at \hyperref[https://github.com/Tarrasch]{github}.
   \item Maintaining a Jenkins continuous integration server 
    and webmastering my university's student website.
   \item Currently a supplemental instruction leader in math at the university.
   \item Native Swedish, good English and mother tongue Persian. Some German.
 \end{itemize}
 
\section{EDUCATION} 
 \noindent Completed 3 of 5 years of M.Sc. in CS
  at Chalmers University of Technology.
 
\section{WORKING EXPERIENCE}
\emph{Spotify Summer 2011}, Stockholm, Sweden
\vspace{0.2in}
   \begin{itemize} % \itemsep -2pt  % reduce space between items
   \item Designed and implemented a large test 
    suite for their C API libspotify.
    This led to fixing many bugs and giving an 
    invaluable code coverage for the code base.
 \end{itemize}


\emph{Silobreaker Summer 2010 and 2009}, Stockholm, Sweden
\vspace{0.2in}
 \begin{itemize} % \itemsep -2pt  % reduce space between items
  \item Built a mobile site, used a Support Vector Machine, wrote a tokenizer,
   programmed a GUI.
  \item Became acquainted with Scrum and Test Driven Development.
\end{itemize} 

\section{OTHER MERITS}

   \begin{itemize} % \itemsep -2pt  % reduce space between items
   \item European Robotics Championship 2010 in Vienna.
    Participated with a line follower.
   \item Largely helping out with the high school programming contest in Sweden.
    Problem setting and traveling abroad as a team leader.
    This is work done out of good will and without profit.
 \end{itemize}

\section{ACTIVITIES} 
 
I enjoy Chess, play squash and practice the harmonica.
I regularly participate in extracurricular
activities at the university.
 

\end{resume}
\end{document}











